---
title: "f"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. I could not find the use of sliderinput() within the tennis app. However, sliderinput() and numericinput() take the same parameteres the only difference is numeric is a number scale and slider is a physical slider. 

2.   sliderInput("animation", "Looping Animation:",
                  min = 1, max = 2000,
                  value = 1000, step = 5,
                  animate =
                    animationOptions(interval = 300, loop = TRUE))
                    
Again unsure where I could add the slider for tennis app but this is how I would implement such a slider. 


```{r}
library(tidyverse)
library(readr)
wta_df <- read_csv("Data/data/wta_matches_2019.csv")
atp_df <- read_csv("Data/data/atp_matches_2019.csv")

both_df <- bind_rows(atp_df, wta_df)

both_long <- both_df %>% pivot_longer(c(winner_name, loser_name))

## only keep players who have player over 50 matches
both_n50 <- both_long %>% group_by(value) %>% count() %>%
  filter(n > 50)

## construct various statistics
major_tennis <- semi_join(both_long, both_n50, by = c("value"))
major_tennis <- major_tennis %>% mutate(w_svperc = 100 * w_1stIn / w_svpt,
                                        l_svperc = 100 * l_1stIn / l_svpt,
                                        w_firstwon = 100 * w_1stWon / w_1stIn,
                                        l_firstwon = 100 * l_1stWon / l_1stIn,
                                        w_secondwon = 100 * w_2ndWon / (w_svpt - w_1stIn),
                                        l_secondwon = 100 * l_2ndWon / (l_svpt - l_1stIn))

major_tennis_w <- major_tennis %>% filter(name == "winner_name")
major_tennis_l <- major_tennis %>% filter(name == "loser_name")

w_small <- major_tennis_w %>% select(value, winner_seed, w_ace, w_df, w_svperc,
                                     w_firstwon, w_secondwon) %>%
  rename(seed = winner_seed, ace = w_ace, df = w_df, svperc = w_svperc,
         firstwon = w_firstwon, secondwon = w_secondwon)

l_small <- major_tennis_l %>% select(value, loser_seed, l_ace, l_df, l_svperc, l_firstwon, l_secondwon)  %>%
  rename(seed = loser_seed, ace = l_ace, df = l_df, svperc = l_svperc,
         firstwon = l_firstwon, secondwon = l_secondwon)

df <- bind_rows(w_small, l_small) %>%
  rename(player = "value")
df

## step 1
df_oneplayer <- df %>% filter(player == "Daniil Medvedev")
ggplot(data = df_oneplayer, aes(x = ace)) +
  geom_histogram(colour = "black", fill = "white", bins = 15)

library(shiny)

ui <- fluidPage(
  sidebarLayout(
    sidebarPanel(selectizeInput(inputId = "playerselect",
                                label = "Choose a Player",
                                choices = levels(factor(df$player))),
                 radioButtons(inputId = "varselect",
                              label = "Choose a Variable",
                              choices = names(df)[c(3, 4, 5, 6, 7)])),
    mainPanel(plotOutput("histplot"))
  )
)

server <- function(input, output, session) {
  
  df_oneplayer <- reactive({
    df %>% filter(player == input$playerselect)
  })
  
  
  output$histplot <- renderPlot({
    ggplot(data = df_oneplayer(), aes(x = .data[[input$varselect]])) +
      geom_histogram(colour = "black", fill = "white", bins = 15)
  })
}

shinyApp(ui, server)
```
3.

```{r}
#created a new data set with column names math stat and CS
select <- df %>% filter(major1 == "MATH" | major1 == "STAT"| 
                          major1 == "CS") %>%
  pivot_wider(names_from = major1, values_from = major2)
```



```{r}
library(tidyverse)

library(readxl)
df <- read_excel("Data/data/slu_graduates_17_21.xlsx")


## fixes error in the data
df <- df %>% mutate(across(everything(),
                           .fns = ~replace(., . ==  "STATS" , "STAT")))
df <- df %>% filter(major1 == "MATH" | major1 == "STAT"| 
                          major1 == "CS")

df_long <- df %>% pivot_longer(3:8, names_to = "type", values_to = "discipline")
df_major <- df_long %>% 
  filter(type == "major1" | type == "major2" | type == "major3")

df_stat <- df_major %>% filter(discipline == "STAT") 
df_statfull <- semi_join(df_long, df_stat, by = "adm_id") %>%
  filter(type == "major1" |
           type == "major2" | 
           type == "major3")

df_nostat <- df_statfull %>% filter(discipline != "STAT" &
                                      !is.na(discipline)) %>%
  group_by(discipline) %>%
  summarise(nstudent = n()) %>%
  mutate(discipline = fct_reorder(discipline, nstudent))

ggplot(data = df_nostat, aes(x = discipline, y = nstudent)) +
  geom_col() +
  coord_flip()

df$major1
library(shiny)


# tried removing selectized input and replacing with radio buttons but could not get chunk to run.
ui <- fluidPage(
  sidebarLayout(
    sidebarPanel(radioButtons(inputId = "varselect",
                              label = "Choose a Major",
                            choices = names(select)[c(7,8,9)]))),
    mainPanel(plotOutput(outputId = "majorplot"))
  )


server <- function(input, output, session) {
  
  df_update <- reactive({
    df_stat <- df_major %>% filter(discipline == input$majorchoice) 
    
    
    df_statfull <- semi_join(df_long, df_stat, by = "adm_id") %>%
      filter(type == "major1" |
               type == "major2" | 
               type == "major3")
    
    df_nostat <- df_statfull %>% filter(discipline != input$majorchoice &
                                          !is.na(discipline)) %>%
      group_by(discipline) %>%
      summarise(nstudent = n()) %>%
      mutate(discipline = fct_reorder(discipline, nstudent))
  })
  
  
  output$majorplot <- renderPlot({
    ggplot(data = df_update(), aes(x = discipline, y = nstudent)) +
      geom_col() +
      coord_flip()
  })
}

shinyApp(ui, server)
```

4.
```{r}
## create datatable with sex and major
library(ggplot2)
my_data <- ggplot(data = df, aes(x = major1, y =sex)) +
  geom_point(size = 3)
```

```{r}
library(tidyverse)
library(readxl)
df <- read_excel("Data/data/slu_graduates_17_21.xlsx")


## fixes error in the data
df <- df %>% mutate(across(everything(),
                           .fns = ~replace(., . ==  "STATS" , "STAT")))

df_long <- df %>% pivot_longer(3:8, names_to = "type", values_to = "discipline")
df_major <- df_long %>% 
  filter(type == "major1" | type == "major2" | type == "major3")

df_stat <- df_major %>% filter(discipline == "STAT") 
df_statfull <- semi_join(df_long, df_stat, by = "adm_id") %>%
  filter(type == "major1" |
           type == "major2" | 
           type == "major3")

df_nostat <- df_statfull %>% filter(discipline != "STAT" &
                                      !is.na(discipline)) %>%
  group_by(discipline) %>%
  summarise(nstudent = n()) %>%
  mutate(discipline = fct_reorder(discipline, nstudent))

ggplot(data = df_nostat, aes(x = discipline, y = nstudent)) +
  geom_col() +
  coord_flip()

df$major1
library(shiny)

ui <- fluidPage(
  tableOutput("static"),
  sidebarLayout(
    sidebarPanel(selectizeInput(inputId = "majorchoice",
                             label = "Choose a Major",
                             choices = factor(df$major1))),
    mainPanel(plotOutput(outputId = "majorplot"))
  )
)

server <- function(input, output, session) {
  # call table and try to print 
    output$static <- renderTable(head(my_data))
  
  df_update <- reactive({
    df_stat <- df_major %>% filter(discipline == input$majorchoice) 
    
    
    df_statfull <- semi_join(df_long, df_stat, by = "adm_id") %>%
      filter(type == "major1" |
               type == "major2" | 
               type == "major3")
    
    df_nostat <- df_statfull %>% filter(discipline != input$majorchoice &
                                          !is.na(discipline)) %>%
      group_by(discipline) %>%
      summarise(nstudent = n()) %>%
      mutate(discipline = fct_reorder(discipline, nstudent))
  })
  
  
  output$majorplot <- renderPlot({
    ggplot(data = df_update(), aes(x = discipline, y = nstudent)) +
      geom_col() +
      coord_flip()
  })
}

shinyApp(ui, server)
```


