---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


“All work presented is my own, and I have followed all rules for collaboration.”

-Caleb Hamblen


Construct a Shiny app for any data set that we have worked with so far (besides SLU Majors and Tennis) or for any data set you used in STAT/DATA 234. Thirteen points will be given for Shiny apps that:

run,
have at least 2 different inputs,
have at least 1 plot output that looks presentable (e.g. appropriate labels, colour scale, and makes sense to construct).
Then, write a 2 sentence description about the purpose of your app (2 points).


```{r}
library(readr)
library(tidyverse)
# error saying directory not found even tho properly loads in data set.
pokemon_full <- read_csv("Data/data/pokemon_full.csv")
library(shiny)

var_choices <- names(pokemon_full)[c(4:9)]


ui <- fluidPage(
  sidebarLayout(sidebarPanel(
    selectizeInput("typechoice",
                   label = "Choose a Type", choices = levels(factor(pokemon_full$Type)),
                   selected = "Grass"),
    radioButtons("varchoice", label = "Choose a Statistic",
                 choices = var_choices),
    sliderInput("binnumber", label = "Choose a Number of Bins", 
                min = 1, max = 50, value = 15, step = 1)),
    mainPanel(plotOutput("histgraph"),
              tableOutput("wintab"))
  )
)

server <- function(input, output, session) {
  
  pokemon_full_sub <- reactive({
    pokemon_full %>% filter(Type == input$typechoice)
  })
  
  hist_plot <- reactive({
    base_plot <- ggplot(pokemon_full_sub(), aes(x = .data[[input$varchoice]]))
    
    
    if (is.numeric(pokemon_full_sub()[[input$varchoice]]) == TRUE) {
      
      base_plot + geom_histogram(colour = "black", fill = "white",
                                 bins = input$binnumber) +
        theme_minimal(base_size = 22)
    } else if (is.character(pokemon_full_sub()[[input$varchoice]])) {
      base_plot + geom_bar(colour = "black", fill = "white") +
        theme_minimal(base_size = 22) +
        coord_flip()
    }
  })
  
  
  output$histgraph <- renderPlot({
    hist_plot()
  })
  
  output$wintab <- renderTable({
    table(pokemon_full_sub()$result)
  })
  
}


shinyApp(ui, server)
```

The purpose of my app is to graph the base stats of a pokemon type of the users choosing. Then the reader can compare the differences between say Grass types - HP vs Fire types HP. The user can also adjust the number of bins in the graph. 
