---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```


“All work presented is my own, and I have followed all rules for collaboration.”



Use the STAT 113 survey data set to explore the trend in the popularity of Facebook over time. Do this in 2 ways:

```{r}
library(readr)
library(tidyverse)
stat113_survey <- read_csv("Data/data/stat113_survey.csv")

```

(7 points). Construct a graph that uses the number of Facebook friends each student has.

```{r}
statsurvey_FB <- stat113_survey %>% filter(!is.na(Facebook))%>% group_by(time_both) %>%
  mutate(bothtime = fct_reorder(time_both, Facebook))

ggplot(data = statsurvey_FB, aes(x = time_both, y = Facebook)) +
  geom_boxplot() +
  coord_flip()

```


(7 points). Construct a graph that uses the proportion of students that have Facebook (assuming that 0 friends means that the student does not have a Facebook account and more than 0 friends means that the student does have a Facebook account).

```{r}
statsurvey_prop <- statsurvey_FB %>% group_by(time_both) %>%
  summarise(nyes = sum(Facebook > 0),
            nno = sum(Facebook == 0)) %>%
  mutate(ntotal = nyes + nno,
         FB_percentage = 100 * nyes / ntotal) %>%
  mutate(Group_PCT = fct_reorder(time_both, FB_percentage))



ggplot(data = statsurvey_prop, aes(x = time_both, y = FB_percentage)) +
  geom_point() +
  coord_flip() +
  labs(y = "Facebook Usage Percentage")
```



