---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Statement of Integrity: Copy and paste the following statement and then sign your name (by typing it) on the line below.

“All work presented is my own. I have not communicated with or worked with anyone else on this quiz.”

Caleb Hamblen

Collaboration Reminder: You may not communicate with or work with anyone else on this quiz, but you may use any of our course materials or materials on the Internet.



Question 1 (20 points). Examine the alcohol.csv data set that you may have used as an introductory data set in STAT/DATA 234:

```{r}


library(readr)
alcohol_df <- read_csv("Stat4005_DataVis/Data/data/alcohol.csv")


library(mapproj)
library(maps)
library(tidyverse)
world_df <- ggplot2::map_data("world")

beer_world <- left_join(world_df, alcohol_df, by = c("region" = "country"))


ggplot(data = beer_world,
            mapping = aes(x = long, y = lat,
                          group = group)) +
  geom_polygon(colour = "black", aes(fill = beer_servings)) +
  coord_map(xlim=c(-180,180),projection = "globular") +
  theme(axis.text = element_blank()) +
  theme_void()+
  scale_fill_distiller(type = "div", direction = 1)

  
```



The data set has the following variables on countries throughout the world:

Construct a map of the beer_servings variable. You should choose an appropriate projection and change the default colour scheme of your plot.

Question 2 (5 points). Give an example of a question of interest about the alcohol data where you would want to construct a visualization other than a map to answer the question. What type of visualization would you construct instead?

If you were looking at annual beers drank a year by country(in particular by continent) you could create a faceted bar plot by continent. Then you could see the countries within each region and the distribution within each country between years. 
