---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

“All work presented is my own. I have not communicated with or worked with anyone else on this exam.”


Caleb Hamblen

1.
a) uses data, mapping, geom, stat, and coord function
b) One of the main points is what is a bad visual. SO things that are hard to read or compare are "worse". SO ordering them in descending order allows for easy comparisons.
c) You cannot remove zero from a bar plot because it is a count. When removing the beginning it messes with the proportions and confuses the reader because size of bar is being used for scale. Dot plots do not use length as a representation and therefore are okay to remove.

2.
my data folder is nested into another data folder and when I knit it says the location is not real. 

3.
One thing I learned about ethics is when to include 0. When using barplot it is important to always include 0 since bar plots work on length. If a plot is twice as long as another we tend to expect it to have twice the value. But when starting not at 0 this is not the case. 

4.
```{r}
library(maps)
library(tidyverse)
library(here)

election_df <- read_csv(here("Data/data/2020_county_pres.csv")) %>%
  group_by(state_name) %>%
  summarise(total_gop = sum(votes_gop),
            total_dem = sum(votes_dem)) %>%
  mutate(percent_gop = 100 * total_gop / (total_gop + total_dem)) %>%
  mutate(state_name = str_to_lower(state_name))

state_df <- ggplot2::map_data("state")

state_full <- left_join(state_df, election_df, by = c("region" = "state_name"))

ggplot(data = state_full, aes(x = long, y = lat, group = group)) +
  geom_polygon(colour = "black", aes(fill = percent_gop)) +
  coord_map(projection = "albers", lat0 = 39, lat1 = 45) +
  theme_void() +
  scale_fill_viridis_c()
```
b) Because of group and order. Group tells R which polygons to draw, and order tells it what order to draw each little line segment to make up the borders.

5.

```{r}
library(shiny)
library(tidyverse)
library(ggrepel)
library(here)
alcohol_df <- read_csv(here("Data/data/alcohol.csv"))

onecountry_df <- alcohol_df %>% filter(country == "Australia")

ggplot(alcohol_df, aes(x = beer_servings, y = wine_servings)) +
  geom_point() +
  geom_label_repel(data = onecountry_df, aes(label = country)) +
  geom_point(data = onecountry_df, size = 3, shape = 1)
```

```{r}
library(shiny)

var_choices <- names(alcohol_df)[c(2:4)]



ui <- fluidPage(
  sidebarLayout(
    sidebarPanel(selectizeInput(inputId = "countrychoice",
                                label = "Choose a Country",
                                choices = factor(alcohol_df$country))),
    radioButtons("varchoice", label = "Choose a Statistic",
                 choices = names(var_choices)),
    mainPanel(plotOutput(outputId = "majorplot"))
  )
)

server <- function(input, output, session) {
  
  df_sub <- reactive({
    df_one <- alcohol_df %>% filter(country == input$countrychoice) 
  })
  
  df_update <- reactive({
     base_plot <- ggplot(df_sub(), 
                         aes(x = beer_servings, y = wine_servings))+
  geom_point() +
  geom_label_repel(data = df_sub(), aes(label = country)) +
  geom_point(data = df_sub(), size = 3, shape = 1)
    
  })
  
  df_minor <- reactive({
      base_plot <- ggplot(df_sub(), aes(x = .data[[input$varchoice]]))
      
      base_plot + geom_histogram(colour = "black", fill = "white",
                                 bins = input$binnumber) +
        theme_minimal(base_size = 22)
  })
    
    
  
  
  output$majorplot <- renderPlot({
    df_update()
  })
  
  output$majorplot <- renderPlot({
    df_minor()
  })
  }

shinyApp(ui, server)

```

6.
Reactive graph on paper

7.
```{r}
library(tidyverse)
library(here)
wta_df <- read_csv(here("Data/data/wta_matches_2019.csv"))
wta_long <- wta_df %>% pivot_longer(c(winner_name, loser_name),
                                    names_to = "won_or_lost",
                                    values_to = "player") %>%
  select(won_or_lost, player, everything())
```

```{r}
plus_20 <- wta_long %>% group_by(player) %>% 
  mutate(total = n())%>%              
  filter(total >= 20)

avg_ace<-plus_20 %>% group_by(player,tourney_id) %>%
  summarise(avg_aces = w_ace+ l_ace)%>%
  filter(!is.na(avg_aces))

avg_ace <- avg_ace %>% group_by(player) %>%
  summarise(real = sum(avg_aces)/20)%>%
  filter(real >= 23)

ggplot(data = avg_ace, aes(x=player, y=real)) +
  geom_point() + 
  geom_segment( aes(x=player, xend=player, y=0, yend=real))
```

8.

Lollipop charts hide underlying variability. We can't see the best/worse matches within each player.

b)
```{r}
box_ace<-plus_20 %>% group_by(player,tourney_id) %>%
  summarise(avg_aces = w_ace+ l_ace)%>%
  filter(!is.na(avg_aces))
  

ggplot(data = box_ace, aes(x=player, y=avg_aces)) +
  geom_boxplot()
```



